Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-10-08 Ben_Manuscripts/stochastic_transport/Draft.tex
Initial edits to draft

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories, in order
  to predict solute mean squared displacements (MSDs). With our first model, based
  on the anomalous diffusion literature, we show how solute dynamics can be modeled as
  a fractional diffusion process subordinate to a continuous time random walk.
  We parameterize the distribution of dwell times, hop lengths between dwells and
  correlation between hops. We explore 2 variations of the model. The first variation
  applies a single set of parameters to the solutes and the second applies 2 sets
  of parameters based on the solute's radial distance from the closest pore center.
  Our second model, an adaptation of Markov state models, treats the 
  %MRS4: I don't think this quite captures what is going on, tried to rephrase.
  %system as a Markov process, where we quantify the transitions between a set of 
  %explicitly defined states. 
  configurational state of the system as a Markov process, each of which has state dependent transport behavior.
  We 
  %MRS4: tweaked
  %incorporate 
  fit
  the magnitude and temporal correlation
  of positional fluctuations into each state and transitions between states to gain
  further insight and allow us to predict solute MSDs. We show that our models 
  reasonably reproduce MSDs calculated from molecular simulations. The anomalous 
  diffusion shows superior predictive performance, in many cases 
  %exactly 
  reproducing
  MD results
  %MRS4: added
  well 
  within error. 
  %MRS4: next two sentences seem somewhat repetitive
  We use the parameters of each model to offer additional mechanistic
  insight. These parameters are important for identifying specific differences in 
  solute transport behavior. The differences suggest modifications that can be
  made to LLC membrane monomers in order to increase or reduce selectivity towards a 
  specific solute
  %MRS4: added
  or class of solutes.
  \end{abstract}

@@

  % MRS1: I would start with something more central to the content of the paper - how do solutes move in complex separations membranes?  Let people know right from the start what the paper is about.  This paragraph should still be in the intro, but start with something that captures the main question of the paper. 
  % BJC2: This paragraph will need more tweaking but is the gist of what I'm thinking
  % BJC2: I'm not sure if this is exactly what you meant though
%  Making sense of solute motion in complex separations membranes is central to 
%  understanding transport mechanisms and formulating membrane design principles.
  % MRS3: seems pretty good.  We can tweak later when turning into text; I don't think that it will really affect the logic of the paper. The introduction will be important here to set the stage, but probably more of that will be in the next paragraph.

  Mathematical descriptions of transport in complex separations membranes are a powerful 
  way to understand mechanisms and formulate membrane design principles. 
  %MRS4: are there citations for the above, like reviews?
  The complexity
  of a model generally parallels the complexity of the transport mechanism at hand, 
  well as 
  the transport information the model conveys.
  %the desired outputs. 
  In dense homogeneous membranes, the solution-diffusion 
  model can extract diffusion and partition coefficients and has successfully predicted
  solute transport rates. 
  %MRS4: citation above?
  Analogously, pore-flow models yield predictions of diffusion 
  coefficients and solute transport rates in nanoporous membranes.~\cite{wijmans_solution-diffusion_1995}
  Modern single particle tracking approaches take us beyond continuum modeling and 
  allow us to characterize complex diffusive behavior.~\cite{manzo_review_2015} 
  At the molecular level, one can use molecular dynamics (MD) simulations to study both
  single particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate speculation on the molecular origins of separations
  by attempting to give a more intuitive understanding of how solutes move as a function
  of their environment, in turn suggesting experiments that 
  %should be run.
  could be performed
  % BJC1: tie this paragraph into above by commenting that highly selective membranes
  % often have complex mechanistic reasons that aren't explained by simpler models
  % BJC3:maybe change this paragraph to just be examples of highly selective separations, not
  %MRS4: below - seems to just be about need for selective membranes, not the design of them.
  Facile design
  of highly selective separations membranes is desirable in numerous
  applications. The ability to efficiently separate ions from saline water sources using 
  membranes has been actively pursued for years in an effort to create potable water for 
  people in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable barriers to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
  The speed at which we achieve these or any other selective separation will be 
  heavily influenced by the quality of insights gained by the modeling approaches above.

@@

%  Regardless of which LLC phase ones studies, one must contend with the large chemical design
%  space available to design these types of membranes. 
  We 
  %MRS4: proposed change
  %want to use a molecular model in order to understand how we can leverage the large 
  %chemical space available for LLC monomer design in order to create efficient solute-specific
  %separations. 
  Molecular modeling may make it possible to create efficient solute-specific
  separation membranes using the available chemical space of LLC monomers.
  To date, only a limited subset of LLC monomers have been studied in membrane
  applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, 
  %there have been shown
  they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling 
  %MRS4
  %provides 
  can provide
  the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  %traditional 
  %MRS4: above: some would argue lots of design approaches are traditional, not just Edisonian
  Edisonian design approach.

  In our previous work, we used molecular dynamics (MD) simulations to study the transport
  of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
  %BJC3: not sure the following sentence needs to be said.
  The H\textsubscript{II} is a simpler geometry to model than the Q\textsubscript{I} phase.  
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

@@

  %MRS4: consider more citations below, when you talk about what researchers have done.
  Researchers have developed a rigorous theoretical foundation for describing the 
  motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
  The tools introduced by fractional calculus are instrumental to this theory. They
  allow us to generalize the normally linear diffusion equation to fractional
  derivative orders, providing descriptions of a much more diverse set of behavior.~\cite{klages_anomalous_2008}

  Three well-known classes of behavior leading to anomalous subdiffusion are 
  continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  The theory is frequently used to describe single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
  A CTRW is characterized by a distribution of hop lengths and dwell times, 
  where each each hop is characterized by independent random draws from 
  each distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways 
  and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
  These processes can occur alone or in combination.

% BJC3: omitted because too rigid. Ergodicity is hard to prove with 24 solute trajectories.
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.7\textwidth]{subdiffusion_decision_tree.pdf}
%  \caption{This decision tree, adapted from Meroz and Sokolov~\cite{meroz_toolbox_2015},
%  can be used to isolate potential subdiffusive transport mechanisms based on 
%  single solute trajectories.}\label{fig:decision_tree}
%  \end{figure}

  % BJC2: moved this from below
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. We fit anomalous diffusion models in two ways: 
  %MRS4: can you clarify the sentence below?  Probably something like: uses a single set of parameters in the diffusion equations, etc.
  First, based on a single set of parameters. Second, we use a two-state approach incorporating
  two sets of parameters based on a solute's radial distance from the closest pore center.

  While elegant, pure anomalous diffusion theory may in some cases give only a 
  qualitative understanding of transport mechanisms. 
  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
  %Relating it to molecular scale behavior and examples might help.
  Complex temporal relationships in 
  between hops may have a significant effect on the average MSD. Inhomogeneity of 
  a medium or multiple types of interactions may lead to a number of distinct 
  diffusive regimes. In this case, a state based model may be useful.

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three observed solute trapping mechanisms.
  %MRS4: but yours assume first order state kinetics as well.
  Standard MSMs assume first order kinetics and are typically applied 
  towards determining equilibrium populations of and the transitions between 
  various state configurations.~\cite{bowman_using_2009} 
  %MRS4: this probably needs to be explained more explicitly, that the coordinates of the solute are generated according to the current state. 
  We extend the framework
  to include dynamics within states and between jumps. 
  %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
  That is we parameterize 
  and incorporate into our model the magnitude and temporal correlation of
  fluctuations in solute position while in each state as well as during transitions
  to different states. 
  %Temporal correlation in position has a significant influence on 
  %a solute's mean squared displacement.

@@

%  If we can reproduce the MD MSDs within reason
%  then we can use the parameters of our model to gain additional mechanistic insight.
%  
      %MRS: do the solutes also have some diversity of mechanisms (that were observed previously?)
    %BJC1: Yes. Need to put following into words
    %BJC1: Ranking of time spent in pore region: AcOH > EG > URE > MeOH  (spans 4th most to 3rd least)
    %BJC1: All have high hop frequency which is consistent with fast motion
    %BJC1: Hbonding: Urea barely hbonds. AcOH and EG hbond a lot. AcOH has highest hbond lifetime of all 20 solutes. MeOH on par with all other simple alcohols
    %BJC1: Sodium Association: Urea coordinates with sodium the most of all 20 solutes. AcOH, EG, MeOH spread out of rest of range. Lifetime similar

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region %stopped changing. 
  reaches apparent equilibrium.
  %MRS4: added
  and use only data after that point in our analysis of solute kinetics.
  %We excluded data collected before equilibration
  %from our analysis. 
  We plot the solute partition versus time in Figure~\ref{S-fig:equilibration}
  of the Supporting Information in order to justify our choice of equilibration times
  for each solute.

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  %MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x.  
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle x^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. A value of $\alpha_d < 1$ indicates a subdiffusive process, 
  while values of $\alpha_d = 1$ and $\alpha_d > 0$ are characteristic of Brownian and
  superdiffusive motion respectively.

  %MRS: describe the physical situations in which one would want to choose each of these ways of calculating the MSD.
  %BJC1: For determining ergodicity. Ensemble for determining anomalous exponent. Not sure I'll use ensemble MSD

%  We analyzed both the ensemble-averaged and time-averaged MSDs of the simulated
%  trajectories. The ensemble-averaged MSD measures the displacement of a particle 
%  from its initial position~\cite{meroz_toolbox_2015} and can be written as
%  \begin{equation}
%  \langle x^2(t) \rangle = \langle x(t) - x(0) \rangle^2
%  \label{eqn:ensemble_msd}
%  \end{equation}
%%	\item The average MSD calculated in this way recovers the form of
%%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
%  The time-averaged MSD eliminates initial position dependence by measuring all
%  possible displacements over time lag $\tau$ and can be written as:
%  \begin{equation}
%  \overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
%  \end{equation}
%  where T is the length of the trajectory~\cite{meroz_toolbox_2015}.

  %BJC3: removed ensemble MSD because it's not used
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. 
  %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
  If the underlying 
  subdiffusive process is not ergodic, like a pure CTRW, the time averaged MSD becomes
  linear.~\cite{meroz_toolbox_2015}

%  We determined the ergodicity of the solute trajectories using the ergodicity breaking
%  parameter~\cite{cherstvy_anomalous_2013}:
%  %First, we tested whether the increments of the process were stationary using the augmented Dickey-Fuller test.
%  \begin{equation}
%  EB = \lim_{T \to \infty} \frac{\bigg(\bigg\langle \overline{x^2(T)}^2 \bigg\rangle - \bigg\langle \overline{x^2(T)} \bigg\rangle^2\bigg)}{\bigg\langle \overline{x^2(T)} \bigg\rangle^2}
%  \end{equation}
%  Simply stated, $EB$ quantifies the variance or heterogeneity in the time averaged
%  MSD generated from independent trajectories after ample time has passed. For 
%  ergodic systems, $EB=0$.

  % BJC: Should this be in the results? Lots of figures to show in support of the claims below
  % MRS: can you provide mechanistic reasoning for the below? Then can show the claims for the reasonable possibilities.
  % BJC1: modified this paragraph to parallel the flow chart. I'm still not sure the
  % best place for this. It seems like it belongs in the discussion, but I need to 
  % justify the choice in model so I can write the methods about the chosen models
  % BJC2: Perhaps just say that we think it's sFBM and move the proof to discussion.
  \subsubsection*{Subordinated Fractional Brownian Motion}

  %MRS4: Tweak
  %We believe that 
  The solute motion in the system studied here may be consistent with 
  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
  the leading process is a CTRW. We observe hopping and trapping which is consistent
  with a CTRW, along with negatively correlated hops which is consistent with FBM.

  One can characterize a CTRW process 
  %using 
  by 
  the parameters which describe its dwell 
  time and hop length distributions. We used the \texttt{ruptures} python package in 
  order to automatically identify mean shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018} 
  We used the corresponding hop lengths and dwell times between hops to construct 
  empirical distributions.

@@

  %MRS4: should be more clear which of the two kinetics scenarios this next assumption applies to
  \subsubsection*{Multiple Dynamical Modes}

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  For the two mode model, we defined a transition matrix describing the rate at
  which solutes moved between the tail and pore region. To do so, we populated a
  2$\times$2 count matrix by incrementing the appropriate entry by 1 each time step. 
  For example, if we observed the solute in the tails followed by a transition to 
  the pores, we incremented the $(2, 1)$ entry of the count matrix by 1. We generated
  the transition probability matrix from the count matrix by normalizing the 
  entries in each row so that they summed to unity.

  %MRS4: Do you assume Markovian behavior in transitions between the states?  Be explicit.
  \subsubsection*{Simulating Anomalous Diffusion}

  %MRS4: tweaked: otherwise sounds like you simulated all parameters values as well.
  We simulated models with all combinations of 
  the types of 
  dwell and hop length distributions
  described above, which are summarized in Table~\ref{table:anomalous_models}. All models 
  include correlation between hops.
  %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{|c|c|c|}
	  \hline
	  Dwell Distribution                & Hop Length Distribution & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
	  \end{tabular}
	  \caption{We tested models with various modifications to the dwell and hop
	  length distributions. We incorporate correlation structure into all models.}\label{table:anomalous_models}
 \end{table}

>>>>

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories, in order
  to predict solute mean squared displacements (MSDs). With our first model, based
  on the anomalous diffusion literature, we show how solute dynamics can be modeled as
  a fractional diffusion process subordinate to a continuous time random walk.
  We parameterize the distribution of dwell times, hop lengths between dwells and
  correlation between hops. We explore 2 variations of the model. The first variation
  applies a single set of parameters to the solutes and the second applies 2 sets
  of parameters based on the solute's radial distance from the closest pore center.
  Our second model, an adaptation of Markov state models, treats the configurational
  state of the system as a Markov process, each of which has state dependent 
  transport behavior. For each state and transition between states, we parameterized
  the distribution and temporal correlation structure of positional fluctuations as
  a means of characterization and to allow us to predict solute MSDs.
  We show that our models reasonably reproduce MSDs calculated from molecular 
  simulations. The anomalous diffusion model shows superior predictive performance, 
  in many cases reproducing MD results well within error. Finally, we use the 
  parameters of each model to identify specific differences in solute transport
  behavior which can help suggest modifications that can be made to LLC membrane 
  monomers in order to increase or reduce selectivity towards a specific solute
  or class of solutes.

  \end{abstract}

@@

  Mathematical descriptions of transport in complex separations membranes are 
  a powerful way to understand mechanisms and formulate membrane design principles. 
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  The complexity of a model generally parallels the complexity of the transport 
  mechanism at hand, as well as the transport information the model conveys.
  In dense homogeneous membranes, the solution-diffusion model can extract 
  diffusion and partition coefficients and has successfully predicted solute 
  transport rates.~\cite{wijmans_solution-diffusion_1995} Analogously, pore-flow
  models yield predictions of diffusion coefficients and solute transport rates 
  in nanoporous membranes.~\cite{paul_diffusive_1974} Modern single particle 
  tracking approaches take us beyond continuum modeling and allow us to 
  characterize complex diffusive behavior.~\cite{manzo_review_2015} At the molecular
  level, one can use molecular dynamics (MD) simulations to study both single 
  particle dynamics and bulk transport properties with atomic-level insight.~\cite{coscia_chemically_2019,maginn_best_2018}
  All of these approaches facilitate speculation on the molecular origins of separations
  by attempting to give a more intuitive understanding of how solutes move as a function
  of their environment, in turn suggesting experiments that could be performed.

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable barriers to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
  The speed at which we achieve these or any other selective separation will be 
  heavily influenced by the quality of insights gained by the modeling approaches above.

@@

  Molecular modeling may make it possible to create efficient solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied in membrane applications.
  ~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

  In our previous work, we used molecular dynamics (MD) simulations to study the transport
  of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
  The H\textsubscript{II} is a simpler geometry to model than the Q\textsubscript{I} phase.  
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

@@

  %MRS4: consider more citations below, when you talk about what researchers have done.
  %BJC4: added citations of prominent anomalous diffusion work
  Researchers have developed a rigorous theoretical foundation for describing the 
  motion of particles exhibiting non-Brownian, or anomalous, transport behavior.
  ~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools introduced by 
  fractional calculus are instrumental to this theory.~\cite{gorenflo_fractional_1997}
  They allow us to generalize the normally linear diffusion equation to fractional
  derivative orders, providing descriptions of a much more diverse set of behavior.~\cite{klages_anomalous_2008}

  Three well-known classes of behavior leading to anomalous subdiffusion are 
  continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  The theory is frequently used to describe single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
  A CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories are characterized by independent random draws from 
  each distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways 
  and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
  These processes can occur alone or in combination.

  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. We fit anomalous diffusion models in two ways: 
  %MRS4: can you clarify the sentence below?  Probably something like: uses a single set of parameters in the diffusion equations, etc.
  %BJC4: see if below helps.
  %First, based on a single set of parameters. 
  First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized anomalous diffusion model. Second, we use a two-state approach
  extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center.

  While elegant, pure anomalous diffusion theory may in some cases give only a 
  qualitative understanding of transport mechanisms. 
  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
  %Relating it to molecular scale behavior and examples might help.
  %BJC4: mention ageing
  %BJC4: ?
  Complex temporal relationships in 
  between hops may have a significant effect on the average MSD. Inhomogeneity of 
  a medium or multiple types of interactions may lead to a number of distinct 
  diffusive regimes. In this case, a state based model may be useful.

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three observed solute trapping mechanisms.  
  Standard MSMs are typically applied towards determining equilibrium populations
  of and the transitions between various state configurations.~\cite{bowman_using_2009} 
  %MRS4: this probably needs to be explained more explicitly, that the coordinates 
  %of the solute are generated according to the current state. 
  %BJC4: made more explicit.
  %We extend the framework
  %to include dynamics within states and between jumps. 
  We extend the framework to include state-dependent fluctuations and correlations in 
  solute position. 
  %MRS4: It makes sense to me what the below is, but probably isn't clear enough for others. 
  %BJC4: rephrased
%  That is we parameterize 
%  and incorporate into our model the magnitude and temporal correlation of
%  fluctuations in solute position while in each state as well as during transitions
%  to different states. 
  That is the magnitudes of a solute's fluctuations from its average trapped 
  position and the degree of correlation with its previous fluctuations is 
  defined by the parameters of its current state.

@@

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plotted the solute partition versus time in
  Figure~\ref{S-fig:equilibration} of the Supporting Information in order to justify 
  our choice of equilibration times for each solute.

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
  % BJC4: I think it'll be less confusing to me writing it to change it to z. Is it worth
  % explicitly stating that z is the positional coordinate.
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. A value of $\alpha_d < 1$ indicates a subdiffusive process, 
  while values of $\alpha_d = 1$ and $\alpha_d > 0$ are characteristic of Brownian and
  superdiffusive motion respectively.

  %BJC3: removed ensemble MSD because it's not used
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. 
  %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
  %BJC4: reworded, defined ergodicity (usually called 'weak' ergodicity breaking in literature) and
  % explained why it's not important for this study.
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. The time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because we it is a more statistically robust measure of the average distance a solute
  travels over time versus the ensemble average. Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

%  of the process is exhibits weak ergodicity breaking due to 
%  If the underlying subdiffusive process is not ergodic, like a pure CTRW, the time
%  averaged MSD becomes linear.

  \subsubsection*{Subordinated Fractional Brownian Motion}

  The solute motion in the system studied here may be consistent with 
  subordinated fractional Brownian motion (sFBM) where the parent process is FBM and 
  the leading process is a CTRW. We observe hopping and trapping which is consistent
  with a CTRW, along with negatively correlated hops which is consistent with FBM.

  One can characterize a CTRW process by the parameters which describe its dwell 
  time and hop length distributions. We used the \texttt{ruptures} python package in 
  order to automatically identify mean shifts in solute trajectories, indicating hops.\cite{truong_ruptures:_2018} 
  We used the corresponding hop lengths and dwell times between hops to construct 
  empirical distributions.

@@

  %MRS4: should be more clear which of the two kinetics scenarios this next assumption applies to
  %BJC4: changed title to clarify that this is anomalous diffusion
  \subsubsection*{Multiple Anomalous Diffusion Regimes}

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  %BJC4: I justified sentence after next. Is there something more I should say? 
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  For the two mode model, we defined a transition matrix describing the rate at
  which solutes moved between the tail and pore region. We assumed Markovian transitions
  between modes, meaning each transition had no memory of previously visited modes. 
  We populated a 2$\times$2 count matrix by incrementing the appropriate entry by 1 each time step. 
  For example, if we observed the solute in the tails followed by a transition to 
  the pores, we incremented the $(2, 1)$ entry of the count matrix by 1. We generated
  the transition probability matrix from the count matrix by normalizing the 
  entries in each row so that they summed to unity.

  %MRS4: Do you assume Markovian behavior in transitions between the states?  Be explicit.
  %BJC4: Yes, added sentence directly after thesis above

  \subsubsection*{Simulating Anomalous Diffusion}

  We simulated models with all combinations of the types of dwell and hop length
  distributions described above, which are summarized in Table~\ref{table:anomalous_models}.
  All models include correlation between hops.
  %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{|c|c|c|}
	  \hline
	  Dwell Distribution                & Hop Length Distribution & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
	  \end{tabular}
	  \caption{We tested models with various modifications to the dwell and hop
	  length distributions. We incorporate correlation structure into all models.}\label{table:anomalous_models}
 \end{table}

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10000 anomalous diffusion trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations. 
  % BJC4: removed following sentence because I talk about aging above
  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
  with corresponding 95\% intervals.
  %BJC3: Not sure if 40 % above is too long. I could do 20
  %MRS4: is there some rule of thumb that could be used to justify the choice?
  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We 
  %MRS4: not quite sure what you mean by incorporating uncertainty. 
  %BJC4: The Dirichlet distribution basically perturbs the transition probabilities
  % by an amount proportional to the number of observations. So things that don't
  % get transition to/from frequently will have higher uncertainty. Output of 
  % draw form Dirichlet distribution sums to 1. It doesn't really change the results
  % much but I think it's good practice. In the 2D case, it is just a beta distribution
  incorporated uncertainty into transition probabilities by drawing samples from a 
  two dimensional Dirichlet distribution (also called a beta distribution) with concentration parameters defined by 
  the count matrix.~\cite{bacallado_bayesian_2009} We drew hops and dwells based on
  the current state of the system.

  %BJC4: already said this earlier
%  We used a single Hurst parameter to describe
%  correlation between hops, independent of the solute's mode. Ideally, each mode
%  would have its own Hurst parameter, but we did not observe enough long sequences
%  of uninterrupted time spent in each mode with which to generate robust
%  autocorrelation functions.
